---
title: "Processed Data"
date: 2023-02-14
output:
  html_document:
    toc: true
    toc_depth: 3
---

# Logic Flow

[Quantitation Reference Powerpoint](https://uflorida-my.sharepoint.com/:p:/g/personal/camden_camacho_ufl_edu/EaVbQvErEnNKpVYSX4BhQ-EB34x2tahj1mSEbT9KeP13_Q?rtime=REwgXe8f20g)

## Calculation Steps

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

# define the global styles of the nodes. We can override these in box if we wish
node [shape = rectangle, style = filled, fillcolor = white]


step1 [label = 'Build the Calibration Curve (see Building the Calibration Section)']
step2 [label = 'Quantifying the Samples (see Quantifying Samples Section)']
step3 [label = 'Produce Data outputs (TBD)']

# edge definitions with the node IDs
step1 -> step2 -> step3
}")
```

### Building the Calibration Curve

#### Calculate Average Peak Ratio

##### Build Average Peak Area Table

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {
    //
    // Defaults
    //

    // Box for entities
    node [shape=none, margin=0]

    // One-to-many relation (from one, to many)
    edge [arrowtail=none, dir=both]

    //
    // Entities
    //
    individual_native_analyte [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>individual_native_analyte</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>individual_native_analyte_peak_area: numeric</td></tr>
        </table>
    >]

    internal_standard [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>internal_standard_peak_area: numeric</td></tr>
        </table>
    >]
    
    extraction_batch_source [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>extraction_batch_source</td></tr>
            // columns
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>internal_standard_mix: text</td></tr>
        </table>
    >]

    native_analyte_internal_standard_mapping [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_internal_standard_mapping</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
        </table>
    >]

    average_peak_area_ratio_calculation_input [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio_calculation_input</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>individual_native_analyte_peak_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_peak_area: numeric</td></tr>
        </table>
    >]
    
    internal_standard_max_calibration_level [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard_max_calibration_level</td></tr>
            // columns
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>internal_standard_mix: text</td></tr>
            <tr><td align='left'>max_calibration_level: numeric</td></tr>
        </table>
    >]
    
    batch_error_filename [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>batch_error_filename</td></tr>
            // columns
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
        </table>
    >]
    
    
    step2 [label = 'Filter out Configurable Data from Source for a Given Batch
    1. Internal Standard: Remove calibrations above a set max calibration level
    2. Remove a known bad filename', shape = rectangle, style = filled, fillcolor = white]
    


    //
    // Relationships
    //

    individual_native_analyte -> batch_error_filename
    internal_standard -> internal_standard_max_calibration_level
    internal_standard -> extraction_batch_source
    extraction_batch_source -> step2
    batch_error_filename -> step2
    internal_standard_max_calibration_level-> step2
    
    step2 -> native_analyte_internal_standard_mapping
    native_analyte_internal_standard_mapping -> average_peak_area_ratio_calculation_input
}")
```

##### Calculate Average Peak Area

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]
node [shape = rectangle, style = filled, fillcolor = white]

sourceSample [label = 'SetX_XXX_XXX_short.XLS', shape = folder, fillcolor = linen]

sourceReference [label = 'Native_analyte_ISmatch_source.xlsx', shape = folder, fillcolor = linen]

average_analyte_peak_area_ratio [label = 'average_analyte_peak_area_ratio', shape = folder, fillcolor = lightblue]

stepFilter [label = 'Filter out Configurable Data from Source for a Given Batch
    1. Internal Standard: Remove calibrations above a set max calibration level
    2. Remove a known bad filename', shape = rectangle, style = filled, fillcolor = white]

step1 [label = 'Join Analyte Peak Area with corresponding Internal Standard Peak Area
Using Reference Native_analyte_ISmatch_source.xlsx to get the associated Internal Standard
Joining on Corresponding Internal Standard + Filename']

step2 [label = 'Calculate Analyte Peak Area Ration
Analyte Peak Area Ratio = Analyte Peak Area / Internal Standard Peak Area']

step3 [label = 'For a given Analyte + Calibration Level, calculate Average Analyte Peak Area Ratio']

sourceReference -> step1
sourceSample -> stepFilter -> step1 -> step2 -> step3 -> average_analyte_peak_area_ratio
}")
```

##### Average Peak Area Ratio Output

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    average_peak_area_ratio_calculation_input [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio_calculation_input</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>individual_native_analyte_peak_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_peak_area: numeric</td></tr>
            <tr><td align='left'>analyte_peak_area_ratio: numeric</td></tr>
        </table>
    >]

    average_peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>average_analyte_peak_area_ratio: numeric</td></tr>
        </table>
    >]

   average_peak_area_ratio_calculation_input -> average_peak_area_ratio
}")
```

#### Calculate Concentration Ratio

##### Build Concentration Ratio Table

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    native_analyte_internal_standard_mapping [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_internal_standard_mapping</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
        </table>
    >]

    native_analyte_concentration [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_concentration</td></tr>
            // columns
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>calibration_mix: text</td></tr>
            <tr><td align='left'>native_analyte_name: text</td></tr>
            <tr><td align='left'>native_analyte_concentration_ppt: numeric</td></tr>
        </table>
    >]

    internal_standard_concentration [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard_concentration</td></tr>
            // columns
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>calibration_mix: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppt: numeric</td></tr>
        </table>
    >]



    concentration_ratio_calculation_input [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>concentration_ratio_calculation_input</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>native_analyte_concentration_ppt: numeric</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppt: numeric</td></tr>
        </table>
    >]


native_analyte_internal_standard_mapping -> concentration_ratio_calculation_input
native_analyte_concentration -> native_analyte_internal_standard_mapping
internal_standard_concentration -> native_analyte_internal_standard_mapping
}")
```

##### Calculate Concentration Ratio

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

node [shape = rectangle, style = filled, fillcolor = white]


sourceCalCurve [label = 'Sep2021Calibration_Curve_source.xlsx', shape = folder, fillcolor = linen]

average_analyte_peak_area_ratio_output [label = 'average_analyte_peak_area_ratio_output', shape = folder, fillcolor = lightblue]

concentration_ratio [label = 'concentration_ratio', shape = folder, fillcolor = lightblue]


step4 [label = 'Join the Average Analyte Peak Area Ratio to
1. Native Analyte Concentration On Native Analyte Name + Calibration Level
2. Internal Standard Concentration On Referenced Internal Standard Name + Calibration Level
']

step5 [label = 'Calculate Concentration Ratio:
Analyte Concentration Ratio = Native Analyte Concentration / Internal Standard Concentration']


sourceCalCurve -> step4
average_analyte_peak_area_ratio_output -> step4
step4 -> step5 -> concentration_ratio

}")
```


##### Concentration Ratio Output

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    concentration_ratio_calculation_input [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>concentration_ratio_calculation_input</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>native_analyte_concentration_ppt: numeric</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppt: numeric</td></tr>
        </table>
    >]

    concentration_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>concentration_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: numeric</td></tr>
            <tr><td align='left'>concentration_ratio: numeric</td></tr>
        </table>
    >]

   concentration_ratio_calculation_input -> concentration_ratio
}")
```

##### Calibration Curve Input

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    analyte_reference_table [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>analyte_reference_table</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>minimum_limit_of_quantitation: text</td></tr>
        </table>
    >]

    average_peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>average_analyte_peak_area_ratio: numeric</td></tr>
        </table>
    >]

    concentration_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>concentration_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: numeric</td></tr>
            <tr><td align='left'>concentration_ratio: numeric</td></tr>
        </table>
    >]

    calibration_curve_input [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_input</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: numeric</td></tr>
            <tr><td align='left'>average_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>analyte_concentration_ratio: numeric</td></tr>
        </table>
    >]

step4 [label = 'Remove Calibration Levels below Limit of Quantitation (LOQ) for each Native Analyte', shape = rectangle, style = filled, fillcolor = white]

average_peak_area_ratio -> step4
concentration_ratio -> step4
analyte_reference_table -> step4

step4 -> calibration_curve_input
}")
```

##### Calculate Calibration Curve

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

node [shape = rectangle, style = filled, fillcolor = white]

calibration_curve_input [label = 'calibration_curve_input', shape = folder, fillcolor = lightblue]

calibration_curve_with_recovery_output [label = 'calibration_curve_with_recovery_output', shape = folder, fillcolor = lightblue]

calibration_curve_no_recovery_output [label = 'calibration_curve_no_recovery_output', shape = folder, fillcolor = lightblue]

calibration_curve_troubleshoot [label = 'calibration_curve_troubleshoot', shape = folder, fillcolor = lightblue]

calibration_recovery_troubleshoot [label = 'calibration_recovery_troubleshoot', shape = folder, fillcolor = lightblue]

step6 [label = 'Calculate slope and intercept of the cal curve:
y-axis = Average Peak Area Ratio
x-axis = Analyte Concentration Ratio']

step62 [label = 'Recalculate slope and intercept of the cal curve after recovery:
y-axis = Average Peak Area Ratio
x-axis = Analyte Concentration Ratio']

step7 [label = 'Is R^2 < 0.99 or R^2 >= 0.99?', shape = diamond]

step8 [label = 'Remove single lower and then upper level until R^2 >= 0.99']

step9 [label = 'Calculate Experimental Cocentration Ratio
Experimental Cocentration Ratio = (Average Peak Area Ratio - Intercept)/Slope
']

step10 [label = 'Calculate Recovery
Recovery = Experimental Cocentration Ratio / Analyte Concentration Ratio
']

step11 [label = '0.8 <= Recovery <= 1.2', shape = diamond]

step12 [label = 'Remove Calibration Levels with out of bounds Recovery Value']

calibration_curve_input -> step6
step6 -> step7

step7 -> calibration_curve_no_recovery_output [label = 'R^2 >= 0.99']
calibration_curve_no_recovery_output -> step9
step7 -> step8  [label = 'R^2 < 0.99']
step9 -> step10 -> step11
step11 -> calibration_curve_with_recovery_output [label = 'All Recovery Values in Bounds']
step11 -> step12 [label = 'Recovery Value(s) out of Bounds']
step8 -> step6
step12 -> step62
step8 -> calibration_curve_troubleshoot
step12 -> calibration_recovery_troubleshoot
step62 -> calibration_curve_with_recovery_output

}")
```

##### Calibration Curve Output

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

  calibration_curve_troubleshoot [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_troubleshoot</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>calibration_range: text</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
        </table>
    >]

  calibration_recovery_troubleshoot [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_recovery_troubleshoot</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>experimental_concentration_ratio: numeric</td></tr>
            <tr><td align='left'>analyte_concentration_ratio: numeric</td></tr>
            <tr><td align='left'>recovery: numeric</td></tr>
        </table>
    >]


    calibration_curve_with_recovery_output [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_with_recovery_output</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>slope: numeric</td></tr>
            <tr><td align='left'>y_intercept: numeric</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
            <tr><td align='left'>calibration_range: text</td></tr>
            <tr><td align='left'>removed_calibration_levels: text</td></tr>
            <tr><td align='left'>minimum_average_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>maximum_average_peak_area_ratio: numeric</td></tr>
        </table>
    >]

    calibration_curve_no_recovery_output [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_no_recovery_output</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>slope: numeric</td></tr>
            <tr><td align='left'>y_intercept: numeric</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
            <tr><td align='left'>calibration_range: text</td></tr>
            <tr><td align='left'>removed_calibration_levels: text</td></tr>
            <tr><td align='left'>minimum_average_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>maximum_average_peak_area_ratio: numeric</td></tr>
        </table>
    >]

}")
```

### Quantifying Samples

#### Build Table for Analyte Concentration Calculation

##### Build Sample Peak Ratio Table

The batch number is noted when processing the sample in order to tie to the appropriate extraction_batch_source.

The filename matches to catridge_number in the extraction_batch_sources file.

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


  // Box for entities
  node [shape=none, margin=0]
  
  batch_error_filename [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>batch_error_filename</td></tr>
            // columns
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
        </table>
    >]

  individual_native_analyte [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>individual_native_analyte</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_area: numeric</td></tr>
        </table>
    >]

  internal_standard [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard</td></tr>
            // columns
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>internal_standard_area: numeric</td></tr>
        </table>
    >]

    native_analyte_internal_standard_mapping [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_internal_standard_mapping</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
        </table>
    >]


  peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>catridge_number: integer</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_area: numeric</td></tr>
            <tr><td align='left'>peak_area_ratio: numeric</td></tr>
        </table>
    >]

    individual_native_analyte -> native_analyte_internal_standard_mapping
    internal_standard -> native_analyte_internal_standard_mapping
    native_analyte_internal_standard_mapping -> batch_error_filename
    batch_error_filename -> peak_area_ratio

}")
```

##### Build Analyte Concentration Calculation Table

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


  // Box for entities
  node [shape=none, margin=0]


  peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>catridge_number: integer</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_area: numeric</td></tr>
            <tr><td align='left'>peak_area_ratio: numeric</td></tr>
        </table>
    >]
    
    batch_error_filename [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>batch_error_filename</td></tr>
            // columns
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
        </table>
    >]


    calibration_curve_output [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_output</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>slope: numeric</td></tr>
            <tr><td align='left'>y_intercept: numeric</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
            <tr><td align='left'>minimum_average_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>maximum_average_peak_area_ratio: numeric</td></tr>
        </table>
    >]

    extraction_batch_source [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>extraction_batch_source</td></tr>
            // columns
            <tr><td align='left'>batch_number: integer</td></tr>
            <tr><td align='left'>catridge_number: integer</td></tr>
            <tr><td align='left'>internal_standard_used: text</td></tr>
        </table>
    >]

    internal_standard_mix [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard_mix</td></tr>
            // columns
            <tr><td align='left'>internal_standard_mix: text (NOT NULL)</td></tr>
            <tr><td align='left'>stock_mix: text (NOT NULL)</td></tr>
            <tr><td align='left'>internal_standard_name: text (NOT NULL)</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppb: float (NOT NULL)</td></tr>
        </table>
    >]

    analyte_concentration_calculation [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>analyte_concentration_calculation</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>internal_standard_used: text</td></tr>
            <tr><td align='left'>internal_standard_concentration_ng (C_IS): numeric</td></tr>
            <tr><td align='left'>slope (m): numeric</td></tr>
            <tr><td align='left'>y_intercept (b): numeric</td></tr>
            <tr><td align='left'>peak_area_ratio (A_R): numeric</td></tr>
            <tr><td align='left'>minimum_average_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>maximum_average_peak_area_ratio: numeric</td></tr>
        </table>
    >]

step2 [label = 'Calculate the Amount of Internal Standard in each Sample
1. Internal Standard Concentration (ng/g) or (ppb) * 1000
2. Internal Standard Concentration (nglL) or (ppt) / 1000000
3. Internal Standard Concentration ng/uL * 25', shape = rectangle, style = filled, fillcolor = white]


    peak_area_ratio -> calibration_curve_output [label = 'Join Calculated Calibration Curve Table \n on Native Analyte Name']
    peak_area_ratio -> extraction_batch_source [label = 'Join Extraction Batch Source \non batch_number and cartridge_number']
    peak_area_ratio -> batch_error_filename [label = 'Remove error filenames']
    extraction_batch_source -> internal_standard_mix [label = 'Join Internal Standard Mix on\nInternal Standard Used and Internal Standard Name']
    peak_area_ratio -> internal_standard_mix
    internal_standard_mix -> step2 -> analyte_concentration_calculation

}")
```

#### Calculate Analyte Concentration (Same calculations for with Recovery and without Recovery Filtering)

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

node [shape = rectangle, style = filled, fillcolor = white]

// sourced tables
isMixSource [label = 'IS_Mix_source.xlsx', shape = folder, fillcolor = linen]
extractionBatchSource [label = 'Extraction_Batches_source.xlsx', shape = folder, fillcolor = linen]

// calcualted tables
peak_area_ratio [label = 'peak_area_ratio', shape = folder, fillcolor = lightblue]
calibration_curve_output [label = 'calibration_curve_output', shape = folder, fillcolor = lightblue]

analyte_concentration_calculation_input [label = 'analyte_concentration_calculation_input', shape = folder, fillcolor = lightblue]



step3 [label = 'C_a = ((A_R - b) / m) * C_IS
C_a = concentration of analyte
A_R = peak area ratio
b = y-intercept of cal curve trendline
m = slope of cal curve trendline
C_IS = concentration of internal standard']

step4 [label = 'Evaluate Calibration_Curve_Range_Category
Area Ratio < Instrument Limit of Detection = <LOD
Area Ratio < Calibration Curve Minimum Average Peak Area Ratio = <LOQ
Area Ratio > Calibration Curve Maximum Average Peak Area Ratio = Above Cal
Area Ratio within bounds = Within Calibration Range
']


peak_area_ratio -> analyte_concentration_calculation_input
calibration_curve_output -> analyte_concentration_calculation_input
extractionBatchSource -> analyte_concentration_calculation_input
isMixSource -> analyte_concentration_calculation_input

analyte_concentration_calculation_input -> step4

step4 -> step3
}")
```

### Produce Data Outputs

#### Build Blank Filtering Table

Build a blank filtering table.


```{r echo=FALSE}
DiagrammeR::grViz("digraph {

  node [shape=none, margin=0]



    // sourced tables
    extractionBatchSource [label = 'Extraction_Batches_source.xlsx', shape = folder, style = filled, fillcolor = linen]
    analyte_concentration_calculation_input [label = 'analyte_concentration_calculation_input', shape = folder, style = filled, fillcolor = lightblue]
    average_peak_area_ratio [label = 'average_peak_area_ratio (for reference)', shape = folder, style = filled, fillcolor = lightblue]
    


    step1 [label = 'Filter to Extraction Blank values from Raw Source data using County == Extraction Blank', shape = rectangle, style = filled, fillcolor = white]

    step2 [label = 'Set NF and <LOD values to 0.0', shape = rectangle, style = filled, fillcolor = white]
    
    calc_lod [label = 'Calculate limit_of_detection_concentration_ng:
    1. Using the configured Limit of Detection calibration value, the LOD average peak area ratio = average_peak_area_ratio for that calibration level
    2. limit_of_detection_concentration_ng = (LOD average peak area ratio - intercept)/slope', shape = rectangle, style = filled, fillcolor = white]
    
    replace_loq [label = 'Replace <LOQ values with limit_of_detection_concentration_ng', shape = rectangle, style = filled, fillcolor = white]
    
    
    step3 [label = 'Calculate average_extraction_blank_analyte_concentration_ng by:
    1. batch_number
    2. individual_native_analyte_name', shape = rectangle, style = filled, fillcolor = white]


    blank_sample_average_analyte_concentration [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>blank_sample_average_analyte_concentration</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>cartridge_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>average_extraction_blank_analyte_concentration_ng: numeric</td></tr>
        </table>
    >]

    extractionBatchSource -> step1
    analyte_concentration_calculation_input -> step1
    
    average_peak_area_ratio -> calc_lod -> replace_loq
    step1 -> calc_lod
    step1 -> step2
    step2 -> step3
    replace_loq -> step3
    step3 -> blank_sample_average_analyte_concentration

}")
```


#### Subtract Blank Filtered Values from

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

  node [shape=none, margin=0]



    // sourced tables
    analyte_concentration_calculation_input [label = 'analyte_concentration_calculation_input', shape = folder, style = filled, fillcolor = linen]
    blank_sample_average_analyte_concentration [label = 'blank_sample_average_analyte_concentration', shape = folder, style = filled, fillcolor = linen]
    
    step1 [label = 'Join blank_sample_average_analyte_concentration to analyte_concentration_calculation_input on
    1. batch_number
    2. cartridge_number
    3. individual_native_analyte_name', shape = rectangle, style = filled, fillcolor = white]
    
    step2 [label = 'Calculate blank_filtered_analyte_concnetration_ng with:
    blank_filtered_analyte_concnetration_ng = analyte_concentration_ng - average_extraction_blank_analyte_concentration_ng', shape = rectangle, style = filled, fillcolor = white]
    
    blank_filtered_analyte_concentration [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>blank_filtered_analyte_concentration</td></tr>
            // columns
            <tr><td align='left'>batch_number: numeric</td></tr>
            <tr><td align='left'>cartridge_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>blank_filtered_analyte_concnetration_ng: numeric</td></tr>
        </table>
    >]


    analyte_concentration_calculation_input -> step1
    blank_sample_average_analyte_concentration -> step1
    step1 -> step2
    step2 -> blank_filtered_analyte_concentration

}")
```