---
title: "Processed Data"
date: 2023-02-14
output:
  html_document:
    toc: true
    toc_depth: 3
---

# Logic Flow

[Quantitation Reference Powerpoint](https://uflorida-my.sharepoint.com/:p:/g/personal/camden_camacho_ufl_edu/EaVbQvErEnNKpVYSX4BhQ-EB34x2tahj1mSEbT9KeP13_Q?rtime=REwgXe8f20g)

## Calculation Steps

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

# define the global styles of the nodes. We can override these in box if we wish
node [shape = rectangle, style = filled, fillcolor = white]


step1 [label = 'Build the Calibration Curve (see Building the Calibration Section)']
step2 [label = 'Quantifying the Samples (see Quantifying Samples Section)']
step3 [label = 'Produce Data outputs (TBD)']

# edge definitions with the node IDs
step1 -> step2 -> step3
}")
```

### Building the Calibration Curve

#### Calculate Average Peak Ratio

##### Build Average Peak Area Table

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {
    //
    // Defaults
    //

    // Box for entities
    node [shape=none, margin=0]

    // One-to-many relation (from one, to many)
    edge [arrowtail=none, dir=both]

    //
    // Entities
    //
    individual_native_analyte [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>individual_native_analyte</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>individual_native_analyte_peak_area: numeric</td></tr>
        </table>
    >]

    internal_standard [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard</td></tr>
            // columns
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>source_file_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>internal_standard_peak_area: numeric</td></tr>
        </table>
    >]

    native_analyte_internal_standard_mapping [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_internal_standard_mapping</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
        </table>
    >]

    average_peak_area_ratio_calculation [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio_calculation</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>source_file_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>individual_native_analyte_peak_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_peak_area: numeric</td></tr>
        </table>
    >]


    //
    // Relationships
    //

    individual_native_analyte -> native_analyte_internal_standard_mapping
    internal_standard -> native_analyte_internal_standard_mapping
    native_analyte_internal_standard_mapping -> average_peak_area_ratio_calculation
}")
```

##### Calculate Average Peak Area

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]
node [shape = rectangle, style = filled, fillcolor = white]

sourceSample [label = 'SetX_XXX_XXX_short.XLS', shape = folder, fillcolor = linen]

sourceReference [label = 'Native_analyte_ISmatch_source.xlsx', shape = folder, fillcolor = linen]

average_analyte_peak_area_ratio [label = 'average_analyte_peak_area_ratio', shape = folder, fillcolor = lightblue]

step1 [label = 'Join Analyte Peak Area with corresponding Internal Standard Peak Area
Using Reference Native_analyte_ISmatch_source.xlsx to get the associated Internal Standard
Joining on Corresponding Internal Standard + Filename']

step2 [label = 'Calculate Analyte Peak Area Ration
Analyte Peak Area Ratio = Analyte Peak Area / Internal Standard Peak Area']

step3 [label = 'For a given Analyte + Calibration Level, calculate Average Analyte Peak Area Ratio']

sourceReference -> step1
sourceSample -> step1 -> step2 -> step3 -> average_analyte_peak_area_ratio
}")
```

##### Average Peak Area Ratio Output

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    average_peak_area_ratio_calculation [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio_calculation</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>replicate_number: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>individual_native_analyte_peak_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_peak_area: numeric</td></tr>
            <tr><td align='left'>analyte_peak_area_ratio: numeric</td></tr>
        </table>
    >]

    average_peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>average_analyte_peak_area_ratio: numeric</td></tr>
        </table>
    >]

   average_peak_area_ratio_calculation -> average_peak_area_ratio
}")
```

#### Calculate Concentration Ratio

##### Build Concentration Ratio Table

```{r, echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    native_analyte_internal_standard_mapping [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_internal_standard_mapping</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
        </table>
    >]

    native_analyte_concentration [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_concentration</td></tr>
            // columns
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>calibration_mix: text</td></tr>
            <tr><td align='left'>native_analyte_name: text</td></tr>
            <tr><td align='left'>native_analyte_concentration_ppt: numeric</td></tr>
        </table>
    >]

    internal_standard_concentration [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard_concentration</td></tr>
            // columns
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>calibration_mix: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppt: numeric</td></tr>
        </table>
    >]



    concentration_ratio_calculation [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>concentration_ratio_calculation</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>average_analyte_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>native_analyte_concentration_ppt: numeric</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppt: numeric</td></tr>
        </table>
    >]


native_analyte_internal_standard_mapping -> concentration_ratio_calculation
native_analyte_concentration -> native_analyte_internal_standard_mapping
internal_standard_concentration -> native_analyte_internal_standard_mapping
}")
```

##### Calculate Concentration Ratio

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

node [shape = rectangle, style = filled, fillcolor = white]


sourceCalCurve [label = 'Sep2021Calibration_Curve_source.xlsx', shape = folder, fillcolor = linen]

average_analyte_peak_area_ratio [label = 'average_analyte_peak_area_ratio', shape = folder, fillcolor = lightblue]

calibration_curve_input [label = 'calibration_curve_input', shape = folder, fillcolor = lightblue]


step4 [label = 'Join the Average Analyte Peak Area Ratio to
1. Native Analyte Concentration On Native Analyte Name + Calibration Level
2. Internal Standard Concentration On Referenced Internal Standard Name + Calibration Level
']

step5 [label = 'Calculate Concentration Ratio:
Analyte Concentration Ratio = Native Analyte Concentration / Internal Standard Concentration']


sourceCalCurve -> step4
average_analyte_peak_area_ratio -> step4
step4 -> step5 -> calibration_curve_input

}")
```

##### Concentration Ratio Calculation Output

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

    average_peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>average_peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>average_analyte_peak_area_ratio: numeric</td></tr>
        </table>
    >]

    concentration_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>concentration_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>concentration_ratio: numeric</td></tr>
        </table>
    >]

    calibration_curve_input [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_input</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>calibration_level: text</td></tr>
            <tr><td align='left'>average_peak_area_ratio: numeric</td></tr>
            <tr><td align='left'>analyte_concentration_ratio: numeric</td></tr>
        </table>
    >]


average_peak_area_ratio -> calibration_curve_input
concentration_ratio -> calibration_curve_input
}")
```

##### Calculate Calibration Curve

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

node [shape = rectangle, style = filled, fillcolor = white]

calibration_curve_input [label = 'calibration_curve_input', shape = folder, fillcolor = lightblue]

calibration_curve_output [label = 'calibration_curve_output', shape = folder, fillcolor = lightblue]

calibration_curve_troubleshoot [label = 'calibration_curve_troubleshoot', shape = folder, fillcolor = lightblue]

step6 [label = 'Calculate slope of the cal curve:
y-axis = Average Peak Area Ratio
x-axis = Analyte Concentration Ratio']

step7 [label = 'Is R^2 < 0.99 or R^2 >= 0.99?', shape = diamond]

step8 [label = 'Remove single lower and then upper level until R^2 >= 0.99']

calibration_curve_input -> step6
step6 -> step7

step7 -> calibration_curve_output [label = 'R^2 >= 0.99']
step7 -> step8  [label = 'R^2 < 0.99']
step8 -> step6
step8 -> calibration_curve_troubleshoot

}")
```

##### Calibration Curve Output

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


    // Box for entities
    node [shape=none, margin=0]

  calibration_curve_troubleshoot [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_troubleshoot</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>calibration_range: text</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
        </table>
    >]


    calibration_curve_output [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_output</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>slope: numeric</td></tr>
            <tr><td align='left'>y_intercept: numeric</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
            <tr><td align='left'>calibration_range: text</td></tr>
            <tr><td align='left'>removed_calibration_levels: text</td></tr>
        </table>
    >]


}")
```

### Quantifying Samples

#### Build Table for Analyte Concentration Calculation

##### Build Sample Peak Ratio Table

The batch number is noted when processing the sample in order to tie to the appropriate extraction_batch_source.

The filename matches to catridge_number in the extraction_batch_sources file.

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


  // Box for entities
  node [shape=none, margin=0]

  individual_native_analyte [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>individual_native_analyte</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_area: numeric</td></tr>
        </table>
    >]

  internal_standard [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard</td></tr>
            // columns
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>filename: text</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>internal_standard_area: numeric</td></tr>
        </table>
    >]

    native_analyte_internal_standard_mapping [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>native_analyte_internal_standard_mapping</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
        </table>
    >]


  peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>catridge_number: integer</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_area: numeric</td></tr>
            <tr><td align='left'>peak_area_ratio: numeric</td></tr>
        </table>
    >]

    individual_native_analyte -> native_analyte_internal_standard_mapping
    internal_standard -> native_analyte_internal_standard_mapping
    native_analyte_internal_standard_mapping -> peak_area_ratio

}")
```

##### Build Analyte Concentration Calculation Table

```{r echo=FALSE}
DiagrammeR::grViz("digraph {


  // Box for entities
  node [shape=none, margin=0]


  peak_area_ratio [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>peak_area_ratio</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>catridge_number: integer</td></tr>
            <tr><td align='left'>batch_number: text</td></tr>
            <tr><td align='left'>individual_native_analyte_area: numeric</td></tr>
            <tr><td align='left'>internal_standard_area: numeric</td></tr>
            <tr><td align='left'>peak_area_ratio: numeric</td></tr>
        </table>
    >]


    calibration_curve_output [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>calibration_curve_output</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>slope: numeric</td></tr>
            <tr><td align='left'>y_intercept: numeric</td></tr>
            <tr><td align='left'>r_squared: numeric</td></tr>
        </table>
    >]

    extraction_batch_source [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>extraction_batch_source</td></tr>
            // columns
            <tr><td align='left'>batch_number: integer</td></tr>
            <tr><td align='left'>catridge_number: integer</td></tr>
            <tr><td align='left'>internal_standard_used: text</td></tr>
        </table>
    >]

    internal_standard_mix [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>internal_standard_mix</td></tr>
            // columns
            <tr><td align='left'>internal_standard_mix: text (NOT NULL)</td></tr>
            <tr><td align='left'>stock_mix: text (NOT NULL)</td></tr>
            <tr><td align='left'>internal_standard_name: text (NOT NULL)</td></tr>
            <tr><td align='left'>internal_standard_concentration_ppb: float (NOT NULL)</td></tr>
        </table>
    >]

    analyte_concentration_calculation [label=<
        <table border='0' cellborder='1' cellspacing='0' cellpadding='4'>
            <tr><td bgcolor='lightblue'>analyte_concentration_calculation</td></tr>
            // columns
            <tr><td align='left'>individual_native_analyte_name: text</td></tr>
            <tr><td align='left'>internal_standard_name: text</td></tr>
            <tr><td align='left'>internal_standard_used: text</td></tr>
            <tr><td align='left'>internal_standard_concentration_ng (C_IS): numeric</td></tr>
            <tr><td align='left'>slope (m): numeric</td></tr>
            <tr><td align='left'>y_intercept (b): numeric</td></tr>
            <tr><td align='left'>peak_area_ratio (A_R): numeric</td></tr>
        </table>
    >]

step2 [label = 'Calculate the Amount of Internal Standard in each Sample
1. Internal Standard Concentration (ng/g) or (ppb) * 1000
2. Internal Standard Concentration (nglL) or (ppt) / 1000000
3. Internal Standard Concentration ng/uL * 25', shape = rectangle, style = filled, fillcolor = white]


    peak_area_ratio -> calibration_curve_output [label = 'Join Calculated Calibration Curve Table \n on Native Analyte Name']
    peak_area_ratio -> extraction_batch_source [label = 'Join Extraction Batch Source \non batch_number and cartridge_number']
    extraction_batch_source -> internal_standard_mix [label = 'Join Internal Standard Mix on\nInternal Standard Used and Internal Standard Name']
    peak_area_ratio -> internal_standard_mix
    internal_standard_mix -> step2 -> analyte_concentration_calculation

}")
```


#### Calculate Analyte Concentration

```{r echo=FALSE}
DiagrammeR::grViz("digraph {

graph [layout = dot]

node [shape = rectangle, style = filled, fillcolor = white]

// sourced tables
isMixSource [label = 'IS_Mix_source.xlsx', shape = folder, fillcolor = linen]
extractionBatchSource [label = 'Extraction_Batches_source.xlsx', shape = folder, fillcolor = linen]

// calcualted tables
peak_area_ratio [label = 'peak_area_ratio', shape = folder, fillcolor = lightblue]
calibration_curve_output [label = 'calibration_curve_output', shape = folder, fillcolor = lightblue]

analyte_concentration_calculation [label = 'analyte_concentration_calculation', shape = folder, fillcolor = lightblue]



step3 [label = 'C_a = ((A_R - b) / m) * C_IS
C_a = concentration of analyte
A_R = peak area ratio
b = y-intercept of cal curve trendline
m = slope of cal curve trendline
C_IS = concentration of internal standard']

peak_area_ratio -> analyte_concentration_calculation
calibration_curve_output -> analyte_concentration_calculation
extractionBatchSource -> analyte_concentration_calculation
isMixSource -> analyte_concentration_calculation

analyte_concentration_calculation -> step3
}")
```

### Produce Data Outputs

#### Blank Filtering

Produce a variation on the Analyte Concnetration Table except this will include NF values and for QC/Extraction Blank/Field Blanks

Pre1: Produce a data file that includes all of the Extract Blank, even if NF.
1. Remove the average of Extraction Blanks from the other analyte concentrations.


Blank Filtering means to subtract the value in the blank from the sample.

1. Produce an output table that includes all of the blanks noted from the Extraction Batch Sources
