---
title: "Processed Data"
date: 2023-02-14
output: html_document
---

```{r setup}
path_list <- fs::path_split(getwd())[[1]]
path_length <- length(path_list)
path_minus_docs <- path_list[1:(path_length - 1)]
path <- fs::path(path_minus_docs)
project_path <- fs::path_join(path)
knitr::opts_knit$set(root.dir = project_path)
```

```{r include=FALSE}
source("R/ProcessCalibrationCurveSourceFile.R")
source("R/ProcessExtractionBatchSource.R")
source("R/ProcessInternalStandardMixFile.R")
source("R/ProcessRawData.R")
```

# Overview

The Extraction_Batches_source.xlsx, IS_Mix_source.xlsx, and Sep2021Calibration_Curve_source.xlsx have been processed into individual tables that have been optimized for working with programatically.

## Files

### Sep2021Calibration_Curve_source.xlsx

The Sep2021Calibration_Curve_source.xlsx was split into two tables since the upper table was the native analyte concentrations and the lower table was the isotopically-labeled standards concentrations.

```{r echo=TRUE}
analyte_concen_df <- arrow::read_parquet("data/processed/native_analyte_concentration.parquet")

knitr::kable(head(analyte_concen_df, 25))
```

```{r echo=TRUE}
is_label_df <- arrow::read_parquet("data/processed/internal_standard_concentration.parquet")

knitr::kable(head(is_label_df, 25))
```

### Extraction_Batches_source.xlsx

For Extraction_Batches_source.xlsx, all of the excel tabs were combined into a single file.

```{r echo=TRUE}
batch_source_df <- arrow::read_parquet("data/processed/extraction_batch_source.parquet")

knitr::kable(head(batch_source_df, 25))
```

### IS_Mix_source.xlsx

For the IS_Mix_source.xlsx file, I pulled the the isotopically-labeled standards from each tab and put them in a single table.

```{r echo=TRUE}
is_mix_source <- arrow::read_parquet("data/processed/internal_standard_mix.parquet")

knitr::kable(head(is_mix_source, 25))
```

#### Process Raw Data

#### Individual Native Analyte

```{r echo=TRUE}
source_ind_native_analyte <- arrow::read_parquet("data/processed/source/source_data_individual_native_analyte.parquet")

knitr::kable(head(source_ind_native_analyte, 25))
```

#### Internal Standard

```{r echo=TRUE}
source_internal_standard <- arrow::read_parquet("data/processed/source/source_data_internal_standard.parquet")

knitr::kable(head(source_internal_standard, 25))
```
