---
title: "Processed Data"
date: 2023-02-14
output: github_document
---

# Overview

The Extraction_Batches_source.xlsx, IS_Mix_source.xlsx, and Sep2021Calibration_Curve_source.xlsx have been processed into individual tables that have been optimized for working with programatically.

## Files

### Sep2021Calibration_Curve_source.xlsx

The Sep2021Calibration_Curve_source.xlsx was split into two tables since the upper table was the native analyte concentrations and the lower table was the isotopically-labeled standards concentrations.

```{r}
analyte_concen_df <- arrow::read_parquet("../data/processed/analyte_concentrations.parquet")

knitr::kable(head(analyte_concen_df,25))
```

```{r}
is_label_df <- arrow::read_parquet("../data/processed/is_label_source.parquet")

knitr::kable(head(is_label_df,25))
```

### Extraction_Batches_source.xlsx

For Extraction_Batches_source.xlsx, all of the excel tabs were combined into a single file.

```{r}
batch_source_df <- arrow::read_parquet("../data/processed/processed_extract_batch_source.parquet")

knitr::kable(head(batch_source_df,25))
```

### IS_Mix_source.xlsx

For the IS_Mix_source.xlsx file, I pulled the the isotopically-labeled standards from each tab and put them in a single table.

```{r}
is_mix_source <- arrow::read_parquet("../data/processed/is_mix_source.parquet")

knitr::kable(head(is_mix_source,25))
```
